\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2021-06-04 main.tex
Draft paper (#5)
* compile latex

* re write simulations.py to check that the simulated utility is equal to the theoretical

* initial analysis of data

* fixes bug in matlab code

The current code wrote the cooperation rate for the mutant at
each time step instead of the rate of the resident

* run analysis

* check new data output

* use csvwrite instead of writematrix

* tweaks analysis code to fit the new data

* add the functionality to consider more than just the last turn

* scoring turns as a class argument

* test function further

* run black

* some style fixes

* matlab scripts for

\begin{abstract}
Repeated games are vastly used in evolutionary game theory to explain
cooperation in a variety of environments. Although existing models have shaped
our understanding of human cooperation, the often work with idealized
assumptions. In an evolutionary process, individuals imitate other individuals
of the population based on their fitness. It is commonly assumed that an
individual computes their fitness after interacting with a representative sample
of the population, and remembering all the interactions they participated in. In
real life, we do not always remember all our interactions, instead we rather
recall our most recent ones.

Here, we introduce a framework that allows individuals to estimate their fitness
based on a minimum of social information. We explore the difference between the
classical framework and ours using computer simulations. We present results for
the most commonly used classes of symmetric \(2 \times 2\) games. The
simulations show that, in the prisoner's dilemma individuals with limited memory
tend to adopt less generous strategies and they achieve less cooperation than in
the classical scenario. In contrast, in the stag-hunt and the harmony game, the
impact of memory is less striking. Here individuals with limited memory perform
nearly as well as individuals with full memory. Finally, we observe that the
snowdrift game is the only game for which cooperation can be underestimated in
the classical scenario.
\end{abstract}

>>>>

\begin{abstract}
Repeated games are vastly used in evolutionary game theory to explain
cooperation in a variety of environments. Although existing models have shaped
our understanding of human cooperation, they often work with idealized
assumptions. In an evolutionary process, individuals imitate other individuals
of the population based on their fitness. It is commonly assumed that an
individual computes their fitness after interacting with a representative sample
of the population, and remembering all the interactions they participated in. In
real life, we do not always remember all our interactions, instead we rather
recall our most recent ones.

Here, we introduce a framework that allows individuals to estimate their fitness
based on a minimum of social information. We explore the difference between our
framework and the classical framework using computer simulations. We present results for
the most commonly used classes of symmetric \(2 \times 2\) games. The
simulations show that, in the prisoner's dilemma individuals with limited memory
tend to adopt less generous strategies and they achieve less cooperation than in
the classical scenario. In contrast, in the stag-hunt and the harmony game, the
impact of memory is less striking. Here individuals with limited memory perform
nearly as well as individuals with full memory. Finally, we observe that the
snowdrift game is the only game for which cooperation can be underestimated in
the classical scenario.
\end{abstract}

### 2021-06-04 static/expected_stochastic.tex
Draft paper (#5)
* compile latex

* re write simulations.py to check that the simulated utility is equal to the theoretical

* initial analysis of data

* fixes bug in matlab code

The current code wrote the cooperation rate for the mutant at
each time step instead of the rate of the resident

* run analysis

* check new data output

* use csvwrite instead of writematrix

* tweaks analysis code to fit the new data

* add the functionality to consider more than just the last turn

* scoring turns as a class argument

* test function further

* run black

* some style fixes

* matlab scripts for

    \node[fill, circle, label=above:expected, inner sep=2pt] at (5.7, 5.7) {};
    \node[fill, circle, inner sep=2pt] (stochastic1) at (1, 1) {};
    \node[fill, circle, inner sep=2pt] (stochastic2) at (2, 2) {};
    \node[fill, circle, inner sep=2pt] (stochastic3) at (1, 2) {};
    \node[fill, circle, inner sep=2pt] (stochastic4) at (2, 1) {};

    \node[label=left:1] (y1) at (0, 1) {};
    \node[label=below:1] (x1) at (1, 0) {};

    \draw[dotted] (y1)--(1, 1) {};
    \draw[dotted] (x1)--(1, 1) {};

    \node[label=left:2] (y2) at (0, 2) {};
    \node[label=below:2] (x2) at (2, 0) {};

    \draw[dotted] (y2)--(2, 2) {};
    \draw[dotted] (x2)--(2, 2) {};

    \draw[dotted] (y1)--(2, 1) {};
    \draw[dotted] (x1)--(1, 2) {};

\end{tikzpicture}
\end{document}

>>>>

    \node[fill, circle, label=above:expected, inner sep=2pt] at (5.7, 5.7) {};
    \node[fill, circle, label=above:stochastic, inner sep=2pt] (stochastic) at (1, 1) {};
    \node[label=left:1] (y) at (0, 1) {};
    \node[label=below:1] (x) at (1, 0) {};

    \draw[dotted] (y)--(1, 1) {};
    \draw[dotted] (x)--(1, 1) {};
\end{tikzpicture}
\end{document}

### 2021-06-04 static/last_rounds_matches.tex
Draft paper (#5)
* compile latex

* re write simulations.py to check that the simulated utility is equal to the theoretical

* initial analysis of data

* fixes bug in matlab code

The current code wrote the cooperation rate for the mutant at
each time step instead of the rate of the resident

* run analysis

* check new data output

* use csvwrite instead of writematrix

* tweaks analysis code to fit the new data

* add the functionality to consider more than just the last turn

* scoring turns as a class argument

* test function further

* run black

* some style fixes

* matlab scripts for

\begin{document}
\begin{tikzpicture}[->,>=stealth',
    level/.style={sibling distance = 5cm/#1,
    level distance = 1.7cm},
    level 2/.style = {sibling distance = 2cm, level distance=2.8cm},
    every node/.style = {font=\tiny}]
\node [arn_n] {} 
    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$] {} edge from parent node[above left, rotate=30] {$\frac{1}{N - 1}$}}
    child{ node [arn_n, rotate=-30] {} 
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{M} - S_{R}$}] {} edge from parent node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{M}$}] {} edge from parent node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{M} - S_{R}$}] {} edge from parent node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{R}$}] {} edge from parent node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
            edge from parent node[above left, xshift=1em, yshift=-.8em, rotate=-30] {$1 - \frac{1}{N - 1}$}
		}
; 
\end{tikzpicture}
\end{document}

>>>>

\begin{document}
\begin{tikzpicture}[->,>=stealth',
    level/.style={sibling distance = 5cm/#1,
    level distance = 1.7cm},
    level 2/.style = {sibling distance = 2cm, level distance=2.8cm},
    every node/.style = {font=\tiny}]
\node [arn_n] {} 
    child{ node [arn_r, label={[align=center, yshift=-.8cm]role model-learner}] {} edge from parent node[above left, rotate=30] {$\frac{1}{N - 1}$}}
    child{ node [arn_n, rotate=-30] {} 
            child{ node [arn_r, label={[align=center, yshift=-.8cm]role model-resident\\learner - resident}] {} edge from parent node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]role model-resident\\learner - mutant}] {} edge from parent node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]role model-mutant\\  learner - resident}] {} edge from parent node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]role model-mutant\\  learner - mutant}] {} edge from parent node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
            edge from parent node[above left, xshift=1em, yshift=-.8em, rotate=-30] {$1 - \frac{1}{N - 1}$}
		}
; 
\end{tikzpicture}
\end{document}

### 2021-06-04 static/tree.tex
Draft paper (#5)
* compile latex

* re write simulations.py to check that the simulated utility is equal to the theoretical

* initial analysis of data

* fixes bug in matlab code

The current code wrote the cooperation rate for the mutant at
each time step instead of the rate of the resident

* run analysis

* check new data output

* use csvwrite instead of writematrix

* tweaks analysis code to fit the new data

* add the functionality to consider more than just the last turn

* scoring turns as a class argument

* test function further

* run black

* some style fixes

* matlab scripts for

\begin{document}
\begin{tikzpicture}[->,>=stealth',
    level/.style={sibling distance = 7cm/#1,
    level distance = 1.7cm},
    level 2/.style = {sibling distance = 1.9cm, level distance=2.8cm},
    level 3/.style = {sibling distance = 2cm, level distance=1.9cm},
    level 4/.style = {sibling distance = 2cm, level distance=2.8cm},
    every node/.style = {font=\tiny}]
\node [arn_n] {} 
    child{ node [arn_r, label={[align=center, yshift=-.8cm] $S_{R} - S_{R}$}] {} 
    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{M} - S_{R}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{M}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{M} - S_{R}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{R}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
    edge from parent node[above left, xshift=1em, yshift=-.8em, rotate=-30] {$1 - \frac{1}{N - 1}$}}
    child{ node [arn_n, rotate=-30] {} 
            child{ node [arn_r, label={[align=center, yshift=-.8cm] $S_{R} - S_{R}$\\$S_{M} - S_{R}$}] {} 
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{R} - S_{R}$}] {} edge from parent node[above left, rotate=30] {$\frac{1}{N - 1}$}}
            child{ node [arn_n, rotate=-30] {} 
                    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{M} - S_{R}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
                    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{M}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
                    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{M} - S_{R}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
                    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{R}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
                    edge from parent node[above left, xshift=1em, yshift=-.8em, rotate=-30] {$1 - \frac{1}{N - 1}$}
            }
            edge from parent node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{M}$}] {} edge from parent node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{M} - S_{R}$}] {} edge from parent node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{R}$}] {} edge from parent node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
            edge from parent node[above left, xshift=1em, yshift=-.8em, rotate=-30] {$1 - \frac{1}{N - 1}$}
		}; 
\end{tikzpicture}
\end{document}

>>>>

\begin{document}
\begin{tikzpicture}[->,>=stealth',
    level/.style={sibling distance = 7cm/#1,
    level distance = 2.5cm, sibling distance = 8cm},
    level 2/.style = {sibling distance = 1.9cm, level distance=2.8cm},
    level 3/.style = {sibling distance = 2cm, level distance=1.9cm},
    level 4/.style = {sibling distance = 2cm, level distance=2.8cm},
    every node/.style = {font=\tiny}]
\node [arn_n] {} 
    child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-learner}] {} 
    child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-resident\\learner-resident}] {} edge from parent[densely dashdotted] node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
    child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-resident\\learner-mutant}] {} edge from parent[densely dashdotted] node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
    child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-mutant  \\learner-resident}] {} edge from parent[densely dashdotted] node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
    child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-mutant  \\learner-mutant}] {} edge from parent[densely dashdotted] node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
    edge from parent node[above left, rotate=25] {$\frac{1}{N - 1}$}}
    child{ node [arn_n, rotate=-30] {} 
            child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-resident\\learner-resident}] {} 
            child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-learner}] {} edge from parent node[above left, rotate=50] {$\frac{1}{N - 1}$}}
            child{ node [arn_n, rotate=-30] {} 
                    child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-resident\\learner-resident}] {} edge from parent[densely dashdotted] node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
                    child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-resident\\learner-mutant}] {} edge from parent[densely dashdotted] node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
                    child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-mutant  \\learner-resident}] {} edge from parent[densely dashdotted] node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
                    child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-mutant  \\learner-mutant}] {} edge from parent[densely dashdotted] node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
                    edge from parent node[above left, xshift=1em, yshift=-1.1em, rotate=-55] {$1 - \frac{1}{N - 1}$}
            }
            edge from parent node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-resident\\learner-mutant}] {} edge from parent node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-mutant  \\learner-resident}] {} edge from parent node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm] role model-mutant  \\learner-mutant}] {} edge from parent node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
            edge from parent node[above left, rotate=-30] {$1 - \frac{1}{N - 1}$}
		}; 
\end{tikzpicture}
\end{document}
